Tables/Graphs for Article

### 2018-01-03 article/draft1.tex
added section numbers, reformatted example questions table

\subsubsection*{Whether or not the user made an effort to solve the problem on their own, prior to asking the question}

@@

\subsubsection*{Average frequency ``score'' of a question's tags}

@@

\subsubsection*{Number of characters in the user-defined device title}

@@

\subsubsection*{Average number of characters in a question's tags}

@@

\subsubsection*{Ratio of the number of line breaks to the number of characters in a question's text}

>>>>

\subsubsection*{8.2.5 Whether or not the user made an effort to solve the problem on their own, prior to asking the question}

@@

\subsubsection*{8.2.6 Average frequency ``score'' of a question's tags}

@@

\subsubsection*{8.2.7 Number of characters in the user-defined device title}

@@

\subsubsection*{8.2.8 Average number of characters in a question's tags}

@@

\subsubsection*{8.2.9 Ratio of the number of line breaks to the number of characters in a question's text}
